### 2017-04-06 paper/evaluation.tex
RQ5 - adjusted piechart
pass on RQ4

\subsubsection{Presence of parallelism configurations in build files}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in
\emph{pom.xml} files\Comment{ in the same sample set of \numMedLong{}
  projects}. In principle, some projects can use parallel execution
although that is only activated when developers pass certain
parameters to the build process. For instance, it is possible to
create in Maven multiple configurations in the same build file and
select dynamically which one should be used.

\Mar{I have no clue what you mean here... Why should I care about
  space on build files?  I thought we did this check
  for every project and module.  $\rightarrow$}\Fix{To reduce the
  space of \Fix{x} build files, we considered a subset of \Fix{y}
  build files with the following criteria}: the given \pomf{} file has
\CodeIn{maven-surefire-plugin} plugin declaration and it has an
explicit \CodeIn{configuration} declaration. We automatically parsed
these \Fix{y} files and we used the same approach to classify the
parallelization mode from the parsed configurations as in our previous
analysis. In an initial analysis, we noticed that some projects do not
declare a static value in some parameters, instead, these projects
inform the actual value in the command line. To handle this case, we
computed all valid values for the parameter.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/survey.pdf}                                                                                                                                                   
     \caption{\Luis{todo}}
\end{figure}

>>>>

\subsubsection{Presence of parallelism configurations in build files}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in
\emph{pom.xml} files\Comment{ in the same sample set of \numMedLong{}
projects}. In principle, some projects can use parallel execution
although that is only activated when developers pass certain
parameters to the build process. For instance, it is possible to
create in Maven multiple configurations in the same build file and
select dynamically which one should be used.  We automatically parsed
\Fix{X} build files and we used the same approach to classify the
parsed configurations as in our previous analysis. Initially, we
noticed that our approach was unable to infer the parallel mode in
some projects because these projects do not declare a static value in
some parameters (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parellel>}). For these projects,
it is required to inform additional parameters to enable the parallel
mode in the command line (\eg, \CodeIn{mvn test
-Dparallel.type=classesAndMethods}). \Jbc{We wouldn't have FALSE
NEGATIVES if we considered this $\rightarrow$}To handle this case, we
considered all valid values for the parameter.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\Luis{todo}\label{fig:rq5-answers}}
\end{figure}
